The Heavy Photon Search Test Detector

### 2014-04-24 hps-testrun-nim.tex
Removed illustration comparing to electron run.

The photon beam was generated in the interaction of $5.5$~GeV electrons with a $10^{-4}~X_0$ 
gold radiator located $\approx~9$~m upstream of the PS. The primary beam and scattered 
electrons are deflected away from detectors by the dipole magnet of the photon tagging system. 
During the dedicated HPS Test Run period, the collimated (6.4~mm diameter) photon beam passes 
through the PS pair converter gold foil and later the HPS system as illustrated in 
Figure~\ref{fig:schematic_testrun_vs_erun}.
\begin{figure}[]
\includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
\caption{\small{Illustrative comparison of HPS Test Run photon beam compared to the HPS electron 
beam.}}
\label{fig:schematic_testrun_vs_erun}
\end{figure}
The PS pair converter was located $\approx~77$~cm upstream of the first layer of the SVT.

>>>>

The photon beam was generated in the interaction of $5.5$~GeV electrons with a $10^{-4}~X_0$ 
gold radiator located $\approx~9$~m upstream of the PS. The primary beam and scattered 
electrons are deflected away from detectors by the dipole magnet of the photon tagging system. 
During the dedicated HPS Test Run period, the collimated (6.4~mm diameter) photon beam passes 
through the PS pair converter gold foil and later the HPS system.
%\begin{figure}[]
%\includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
%\caption{\small{Illustrative comparison of HPS Test Run photon beam compared to the HPS electron 
%beam.}}
%\label{fig:schematic_testrun_vs_erun}
%\end{figure}
The PS pair converter was located $\approx~77$~cm upstream of the first layer of the SVT.
